\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
% only for pdflatex
% \input{glyphtounicode}

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underilne
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}


% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - serif
% \titleformat{\section}{
%   \vspace{2pt} \scshape \raggedright\large % header section
% }{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

% TODO EBSERIES
% sans serif sections
\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large % header section
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

% only for pdflatex
% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top row of resume entry
      \textit{#3} & {\color{dark-grey} \small #4}\\ % second row of resume entry
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% CHANGED default leftmargin  0.15 in
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Himanshu Dhakate} \\ \vspace{5pt}
    \small \faPhone* \texttt{+91-9325452858} \hspace{1pt} $|$
    \hspace{1pt} \faEnvelope \hspace{2pt} \texttt{himanshudhakate07@gmail.com} \hspace{1pt} $|$ 
    \hspace{1pt} \faMapMarker* \hspace{2pt}\texttt{Nagpur, Maharashtra}
    \\ \vspace{-3pt}
\end{center}

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Growthpal}{3-May-2021 -- 3-Aug-2021}
      {SWE-Intern}{Pune,Maharashtra}
      \resumeItemListStart
        \resumeItem{Worked on \textbf{Data aggregation} and \textbf{processing pipeline for Data Warehouse.}}
        \resumeItem{Worked on \textbf{architecture design} for analytics program for accessing data.}
         \resumeItem{Built pipelines to bring data from \textbf{AWS Athena} to \textbf{Elastic Search}.}
        \resumeItem{Built the pipeline for \textbf{web-crawling} and periodically updating the data.}
        \resumeItem{Worked on serving ad-hoc data requests from the business team.}
      \resumeItemListEnd

    \resumeSubheading
      {Microsoft Technology Associate}{21-Jan-2019}
      {Student Trainee}{Pune,Maharashtra}
      \resumeItemListStart
        \resumeItem{Learnt some basics of \textbf{Cybersecurity} and \textbf{security layers}.}
        \resumeItem{Learnt about \textbf{operating system security}.}
        \resumeItem{Learnt about \textbf{Network Security} and \textbf{security software}.}

    \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------PROJECTS-----------

\section{PROJECTS}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Path Finding Visualizer}} {}
          \resumeItemListStart
            \resumeItem{Visualizing tool that shows us how path finding algorithms work.}
            \resumeItem{The objective is to show the working of a path finding algorithm visualizing path from start node to the end node.}
	\resumeItem{User can set the position of the start node and end node in given cells.}
	\resumeItem{User can draw walls by clicking or holding mouse over cells. The walls drawn will be avoided by the algorithm.}
	\resumeItem{Beautiful animations to show how path is visualized by an algorithm.}

	\resumeItem{Once the algorithm has found the end cell the optimal path will be illuminated avoiding the obstacles.}
          \resumeItemListEnd
          
        \resumeProjectHeading
          {\textbf{Controlled Conduct Employee System}}{}
          \resumeItemListStart
	\resumeItem{A distributed application, developed to maintain the details of employees working in any organization.}
            \resumeItem{Streamlined daily operations.}
            \resumeItem{Crucial work-related and important personal information about an employee. In a nutshell, it is an online inventory of all employees of an organization.}
 	\resumeItem{Embedded CRM modules using advanced DBMS integration driver.}
	\resumeItem{A well-designed database to store employee information.}
          \resumeItemListEnd
          
      
          
    \resumeSubHeadingListEnd



%-----------EDUCATION-----------
\section {EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Institute of Technology, Karnataka, Surathkal}{2021 - Present}
      {Masters of Technology}{Computer Science and Engineering}
    \resumeSubheading
      {D.Y. Patil College of Engineering, Pune}{2017 - 2021}
      {Bachelor of Engineering}{Information Technology}
      	\resumeItemListStart
    	\resumeItem {\textbf{CGPA}: 8.39 / 10}
       
        \resumeItemListEnd
	\resumeSubheading
      {P.M.B.S Junior College, Nagpur}{2017}
      {Higher Secondary Certificate}{Science}
      	\resumeItemListStart
    	\resumeItem {\textbf{Percentage}: 71.23 / 100}
       
        \resumeItemListEnd
  \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Programming Languages} {: Python, C, C++, HTML/CSS, SQL, Java }\vspace{2pt} \\
     \textbf{Technical}     {: Data Structures and Algorithms, OOPS, Competitive Programming, Web-Scraping, Data analysis, Machine learning}
    }}
 \end{itemize}


%-------------------------------------------
%-----------Achievements-----------
\section {ACHIEVEMENTS}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Graduate Aptitude Test In Engineering(GATE)}{Feb 2021}
      {All India Rank 575 among 101922 candidates}{Computer Science and Engineering}
	\resumeItemListStart
    	\resumeItem {\textbf{Score}: 722 / 1000}
       
        \resumeItemListEnd
    \resumeSubheading
      {TCS National Qualifier Test}{Oct 2020}
      {Scored 1420.34 / 1800 in Aptitude}{}
      	
	\resumeSubheading
      {Microsoft Technology Associate}{Jan 2019}
      {Passed MTA exam in Security Fundamentals}{}
      	
  \resumeSubHeadingListEnd

%-----------Publications-----------
\section {PUBLICATION}
  \begin{itemize}
	\item Bhavika Pawani,  \textbf{Himanshu Dhakate},  Hrishikesh Hajare,  Yusuf Vanwala,   "PATH FINDING VISUALIZER", IJRAR - International Journal of Research and Analytical Reviews (IJRAR), E-ISSN 2348-1269, P- ISSN 2349-5138, Volume.8, Issue 2, Page No pp.273-276, May 2021, Available at : {\href{http://www.ijrar.org/IJRAR21B1503.pdf}{\myuline {link}}}
\end{itemize}
%-----------CERTIFICATIONS-----------
\section {CERTIFICATIONS}
 \begin{itemize}
	\item \textbf{Microsoft Technology Associate} Security Fundamentals
	\item \textbf{Python Programming} Udemy
	\item \textbf{Java Programming} Udemy
\end{itemize}
%---------------Interests-------------------------
\section{INTERESTS}
\begin{multicols}{2}

\begin{itemize}
\item Machine Learning
\item Data Science
\item Artificial Intelligence
\item Competitive Programming
\item Linux
\end{itemize}
\vfill
\columnbreak
\begin{itemize}
\item Cybersecurity
\item Networking
\item Web development
\item Algorithms
\item Cloud Computing
\end{itemize}
\vfill
\end{multicols}
%-------------Languages---------------------
\section{LANGUAGES}
\begin{multicols}{3}
\begin{itemize}
\item English
\end{itemize}
\vfill\null
\columnbreak
\begin{itemize}
\item Hindi
\end{itemize}
\vfill\null
\columnbreak
\begin{itemize}
\item Marathi
\end{itemize}

\end{multicols}


\end{document}
