\chapter{Problem Definition}

In a cloud data center, the client requests
are catered by placing the services in its servers. Such services are deployed through a sandboxing platform to ensure
proper isolation among services from different users. Due to
the lightweight nature, containers have become increasingly
popular to support such sandboxing. However, for supporting
effective and efficient data center resource usage with minimum
resource footprints, improving the containers’ consolidation ratio
is significant for the cloud service providers. Towards this end,
in this paper, we propose an exciting direction to significantly
boost up the consolidation ratio of a data-center environment
by effectively managing the containers’ states. We observe that
many cloudbased application services are event-triggered, so they
remain inactive unless some external service request comes. We
exploit the fact that the containers remain in an idle state when
the underlying service is not active, and thus such idle containers
can be checkpointed unless an external service request comes.
However, the challenge here is to design an efficient mechanism
such that an idle container can be resumed quickly to prevent
the loss of the application’s quality of service (QoS). We have
implemented the system, and the evaluation is performed in
Amazon Elastic Compute Cloud. The experimental results have
shown that the proposed algorithm can manage the containers’
states, ensuring the increase of consolidation ratio.
