\cleardoublepage
%\pagebreak
\phantomsection
\addcontentsline{toc}{chapter}{References}
\begin{thebibliography}{99}

\bibitem{b1}  E. Casalicchio, “Container orchestration: A survey,” in Systems Modeling: Methodologies and Tools. Springer, 2019, pp. 221–235.
\bibitem{b2} F. Rossi, V. Cardellini, and F. L. Presti, “Elastic deployment of software
containers in geo-distributed computing environments,” in Proc. of IEEE
ISCC’19, 2019.
\bibitem{b3}  K. Suo, Y. Zhao, W. Chen, and J. Rao, “An analysis and empirical
study of container networks,” in proceedings of the IEEE Conference
on Computer Communications. IEEE, 2018, pp. 189–197.
\bibitem{b4}  A. Celesti, D. Mulfari, M. Fazio, M. Villari, and A. Puliafito, “Exploring
container virtualization in iot clouds,” in 2016 IEEE International Conference on Smart Computing (SMARTCOMP). IEEE, 2016, pp.1–6.
\bibitem{b5}  A. Celesti, D. Mulfari, A. Galletta, M. Fazio, L. Carnevale, and
M. Villari, “A study on container virtualization for guarantee quality
of service in cloud-of-things,” Future Generation Computer Systems,
vol. 99, pp. 356–364, 2019.
\bibitem{b6}  I. M. A. Jawarneh, P. Bellavista, L. Foschini, G. Martuscelli, R. Montanari, A. Palopoli, and F. Bosi, “Qos and performance metrics for
container-based virtualization in cloud environments,” in Proceedings
of the 20th International Conference on Distributed Computing and
Networking. ACM, 2019, pp. 178–182.
\bibitem{b7}  W. Li, A. Kanso, and A. Gherbi, “Leveraging linux containers to
achieve high availability for cloud services,” in 2015 IEEE International
Conference on Cloud Engineering. IEEE, 2015, pp. 76–83.
\bibitem{b8} D. R. Sangolli, N. M. Ravindrarao, P. C. Patil, T. Palissery, and K. Liu,
“Enabling high availability edge computing platform,” in 2019 7th IEEE
International Conference on Mobile Cloud Computing, Services, and
Engineering (MobileCloud). IEEE, 2019, pp. 85–92.
\bibitem{b9} O. Sukwong, A. Sangpetch, and H. S. Kim, “Sageshift: managing slas
for highly consolidated cloud,” in 2012 Proceedings IEEE INFOCOM.
IEEE, 2012, pp. 208–216
\bibitem{b10} W. Fan, Z. Han, P. Li, J. Zhou, J. Fan, and R. Wang, “A live migration
algorithm for containers based on resource locality,” Journal of Signal
Processing Systems, vol. 91, no. 10, pp. 1077–1089, 2019.
\bibitem{b11}  S. Noor, B. Koehler, A. Steenson, J. Caballero, D. Ellenberger, and
L. Heilman, “Iotdoc: A docker-container based architecture of iotenabled cloud system,” in 3rd IEEE/ACIS International Conference on
Big Data, Cloud Computing, and Data Science Engineering. Springer,
2019, pp. 51–68.
\bibitem{b12} S. Yang, L. Pan, and S. Liu, “An online algorithm for selling your
reserved iaas instances in amazon ec2 marketplace,” in 2019 IEEE
International Conference on Web Services (ICWS). IEEE, 2019, pp.
296–303.
\bibitem{b13}  D. N. Jha, S. Garg, P. P. Jayaraman, R. Buyya, Z. Li, and R. Ranjan, “A
holistic evaluation of docker containers for interfering microservices,”
in 2018 IEEE International Conference on Services Computing (SCC).
IEEE, 2018, pp. 33–40.
\bibitem{b14} S. Pickartz, N. Eiling, S. Lankes, L. Razik, and A. Monti, “Migrating
linux containers using criu,” in International Conference on High
Performance Computing. Springer, 2016, pp. 674–684.

\end{thebibliography}
